%The following papers characterize behaviors of distributed file systems
%on supercomputers:
%\cite{Xie2012}, \cite{Henschel2012}, \cite{Crosby2009}, \cite{Borrill2009}.

%The following papers discuss approaches to better work with distributed 
%file systems given the characters above:
%\cite{Shipman2010}, \cite{Yu2006}, \cite{Tian2011}, \cite{Lofstead2010},
%\cite{Lofstead2009}.

\subsection{Research on Lustre}
Many research papers have focused on the performance issue of 
Lustre file systems. 
%
Here is a selected collection and the main topic of each paper:
Crosby~\cite{Crosby2009} characterized the performance of Lustre file system
on a real supercomputer system;
%
Xie et al.~\cite{Xie2012} specifically characterized output performance
with respect to a number of system parameters;
%
Schwan~\cite{Schwan2003} and Henschel et al.~\cite{Henschel2012} 
demonstrate implementations of Lustre to achieve the best performance
on real systems; and
%
Shipman et al.~\cite{Shipman2010} summarized real lessons learned 
to achieve high performance on a very large scale Lustre file system.


\subsection{Research on GPFS}
GPFS comes with most IBM supercomputers, and also receives intense study
in terms of its performance.
%
Yu et al.~\cite{Yu2006} demonstrated a highly scalable GPFS file system
with satisfactory overall performance;
%
Andrews et al.~\cite{Andrews2005} researched from both theoratical 
and practical sides of the performance of GPFS file system
in an inter-state scale.
%
Further, Freitas et al.~\cite{freitas2011gpfs} reported performance 
of GPFS file system to scan 10 billion files in 43 minutes. 


\subsection{Research on Google File System}
Even Google intends to keep the Google File System restrict
to its own use, it still publishes a few papers discussing the 
performance of Google File System.
%
In addition to the original paper that specifies the design of
Google File System~\cite{ghemawat2003google},
Chang et al.~\cite{Chang2006a} also discusses efforts to make Google
File System better handle structured data;
Ford et al.~\cite{Ford2010a} and Corbett et al.~\cite{Corbett2012a}
also disscussed how Google File System achieves a global scalability.


The rest of this survey paper will elaborate above mentioned studies 
to provide a big picture on performance issues of parallel file systems
and available approaches to best make use of these systems.
