\documentclass[12pt,twocolumn]{IEEEtran11}

\usepackage{times}
\usepackage{epsfig}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{subfigure}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\oddsidemargin -15pt
\evensidemargin -15pt
\leftmargin 0 pt
\topmargin -30pt
\textwidth = 6.9 in
\textheight = 9.0 in

\newcommand{\itembase}{\setlength{\itemsep}{0pt}}
\newcommand{\eg}{{\it e.g., }}
\newcommand{\ie}{{\it i.e., }}
\graphicspath{{FIG/}}

\begin{document}
\bibliographystyle{IEEE}

\title{\Large \bf 
Survey on Implementations and Performance of Three
Distributed File Systems
%Survey on Bottlenecks and Best Practices of Three Implementations of
%Distributed File Systems
}
\author{
Samuel Li\\
Information and Computer Science Department\\
University of Oregon\\
{\em samuelli@cs.uoregon.edu}
}
\maketitle
% You have to do this to suppress page numbers.  Don't ask.
%\pagestyle{empty}
\begin{abstract}
File systems are crucial components of supercomputers and internet-based
service providers, such as Google.
%
Often, file systems consist of many file servers
to provide capacity, performance, and reliability.
%
They are organized as a distributed system 
to provide functionalities of a file system.
%
A distributed file system can have several performance challenges,
due to the distributed nature of the file system itself,
and the high concurrency nature of the supercomputer applications.
%
This survey paper studies architecture and performance issues of three widely 
used file systems: Google File System, GPFS, and Lustre.
%
It provides the readers a better understanding of how distributed system
works, and what to expect from a distributed file system.
%
%The scope of performance issues include identificatin of bottlenecks
%and best approaches to minimize impact of these bottlenecks.
\end{abstract}

%\begin{keywords} 
%Quality Adaptive Streaming, Peer-to-Peer, Internet
%\end{keywords}

\section{Introduction}
\label{sec:intro}
\input{tex/intro}

\section{Architecture of Three File systems}
\label{sec:architecture}
\input{tex/architecture}

\section{Distributed File Partitions}
\label{sec:file_partition}
\input{tex/file_partition}

\section{Achieve an Even Higher Performance}
\label{sec:performance}
\input{tex/performance}


\section{Conclusion}
This paper surveys performance factors of three popular distributed 
file systems: the Google File System (GFS), IBM General Parallel 
File System (GPFS), and Lustre File System.
%
We especially focused on the 1) different architecture design,
2) file partitioning scheme, and 3) efforts and demonstrations to achieve
higher performance using these three file systems.
%
Architecture wise, both GFS and Lustre adopt a master-server mode, whereas
GPFS adopts a decentralized architecture.
%
File partition scheme is more similar among these three file systems, 
with a different in the choice of chunk size.
%
Higher performance is achieved by all three file systems, including 
high robust to failures, high throughput, and high scalability to span
thousands of miles.

%\section{Briefs}
%\label{sec:brief}
%\input{tex/brief}

%% file citations.bib contains all the biblography
\bibliography{main}
\end{document}
